\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Artem Matveev}} & Email: {matfu21@ya.ru}\\
  &Mobile:~~~+7-937-372-81-25 \\
  &\href{https://github.com/matfu-pixel}{Github: ~~github.com/matfu-pixel} \\
  &\href{https://codeforces.com/profile/matfu}{Codeforces: profile/matfu} \\
  &\href{https://www.kaggle.com/dogrose}{Kaggle: dogrose} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AESC MSU Computer class}{Moscow, Russia}
      {Algorithms, data structures, discrete mathematics}{September 2018 - June 2020}

    \resumeSubheading
      {MSU Faculty of Computational Mathematics and Cybernetics, MMP}{Moscow, Russia}
      {Bachelor - Applied mathematics and computer science;  GPA: 4.8}{September 2020 - June 2024}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Programming}{~Python, C++, SQL, Bash}
	\resumeSubItem{Frameworks}{~~~~Sklearn, Numpy, Matplotlib, Pandas, Keras}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~GIT, LaTex}
	\resumeSubItem{Platforms}{~~~~~~~Linux, Windows}
	\resumeSubItem{Soft Skills}{~~~~~~~Leadership, Time Management}
	\resumeSubItem{Languages}{~~~~~~English(upper intermediate)}
    \resumeSubItem{Courses}{~~~~~~~~~~Advanced Data Structures and Algorithms, Algebra and Geometry, Introduction to Machine Learning}    {~~~~~~~~~~~~~~~~~~~~~~Python programming, C++ Programming}
\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Yandex Internship}{Office}
    {Backend Developer (Part-time), Search portal}{February 2022 - July 2022}
    \resumeItemListStart
        \resumeItem{First direction}
          {Optimize data preparation processes and their use in search runtime.}
        \resumeItem{Second direction}
          {Invent and implement new features for machine learning algorithms.}
      \resumeItemListEnd


\resumeSubHeadingListEnd
%-----------School Olympiads-----------------
\section{School Olympiads}
\begin{description}[font=$\bullet$]
\item {(1st level) Open Olympiad of schoolchildren in computer science -
1st degree.}
\item {(1st level) Individual Olympiad of schoolchildren in
computer science and programming - 2nd degree.}
\item (1st level) Olympiad of schoolchildren “Lomonosov” in computer science - 2nd degree.
\item (1st level) All -Siberian Olympiad of schoolchildren in Computer Science
- 3rd degree.
\item All-Russian Olympiad of schoolchildren in Computer science
(regional stage) - 2nd degree.
\item All-Russian team Olympiad of schoolchildren in
programming 2020 - 2nd degree.
\end{description}
\vspace{-5pt}

%-----------University Olympiads-----------------
\section{University Olympiads}
\begin{description}[font=$\bullet$]
\item ACM ICPC (Moscow Regional Competition 2020 November 15
, 2020) - diploma of the 3rd degree.
\item ACM ICPC (Final of Northern Eurasia 2020 on December 13
, 2020) - diploma of the 2nd degree.
\item ACM ICPC (North Eurasia 2020 Contest: Offline 3-4
April 2021) - Certificate of Honor.
\item ACM ICPC (Southern and Volga Russia) Qualifying tournament: NERC
October 10, 2021) - 3rd place.
\item RUCODE 4.0 festival on November 21, 2021 - winner.
\item ACM ICPC (Moscow Regional Competition 2021 December 19
, 2021) - diploma of the 3rd degree.
\item RUCODE 5.0 festival on April 24, 2022 - winner

\end{description}
\vspace{-5pt}

%-----------Machine Learning Contests and Hackathons-----------------
\section{Machine Learning Contests and Hackathons}
\begin{description}[font=$\bullet$]
\item (at the course level) "cmc2021" - contest from A.G. Dyakonov - 3rd place.
\item (at the course level) “Implementation of intersections by sets" - 1st place. 
\item (university level) Hackaton CMC and MTS 2022 - 3rd place
\item Hackaton OVISION HACK - participation

\end{description}
\vspace{-5pt}

%-----------Additional Achievements-----------------
\section{Additional Achievements}
\begin{description}[font=$\bullet$]
\item Participant of joint scientific seminar INM RAS - Huawei
\item Winner of Huawei scholarship, autumn 2021 (3rd semester) and spring 2022 (4rd semester): mathematical essay on the topic "Evaluation of the Intrinsic dimension of data".
\item Twice I receive an increased state scholarship for special achievements in education, 3rd semester and 4rd semester. 
\item I received a scholarship from the Moscow government (1st and 2nd semester).
\vspace{-5pt}

\end{description}

\end{document}
